Price of Anarchy for Mean Field Games

### 2018-08-01 PoA.tex
minor edits prop 4 case 2 Step 2

	We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$, as defined prior to Case 1. Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions. Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u$, $b_2 \eta_t^{b_2} \geq m_\eta$, and $\eta_t^{b_2} \leq M$, for all $t\in[0,T]$.\\

@@

	Step 2: We derive an upper bound for $b_2 SC^{MKV,b_2}$. From equation (\ref{eq:SC_MKV_2}), we have: 
	\begin{equation}
	b_2 SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{2} w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{$=:J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{$=:J_2$}}
	\label{eq:J1_plus_J2_b2_infinity}
	\end{equation}	
	We also notice the following two technical results which are useful for deriving upper bounds for $J_1$ and $J_2$.	
	Let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}$ and $\displaystyle l(t) = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta_u du} ds$. Because for all $b_2 \geq b_2^{*,basic}$ we have $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, then
	\begin{equation}
		b_2 \cdot l(t) \leq b_2 \int_0^t \exp \left(- 2 \frac{b_2}{r + \bar{r}} m_\eta \cdot (t- s) \right) ds = \frac{1}{\kappa_5} (1 - e^{- \kappa b_2 t}) \leq \frac{1}{\kappa_5}, \quad \forall \  t \in [0,T].
	\label{eq:l(t)_upper_bound_b2_infinity}
	\end{equation}
	Besides, with Riccati equation (\ref{eq:riccati_etat}) of $\eta_t^{b_2}$ and the formula of integration by parts, we deduce:
	\begin{IEEEeqnarray*}{rCL}
		 \int_0^T B^{\eta, b_2} (\eta_t^{b_2} )^2 \cdot l(t) dt 
		&= & \int_0^T  (\eta_t^{b_2})' \cdot l(t) dt + \int_0^T \left( -2A^{\eta} \eta_t^{b_2} + C^{\eta} \right) \cdot l(t) dt \nonumber \\
		&\geq & \left[ \eta_T^{b_2} l(T) - \eta_0^{b_2} l(0) - \int_0^T \eta_t^{b_2} \cdot (l(t))' dt \right]  \nonumber \\
		&= & - \int_0^T \eta_t^{b_2} \cdot \left[ l(t)\cdot( - 2 B^{\eta,b_2} \eta_t^{b_2} ) + 1 \right] dt + l(T) D^{\eta} \nonumber \\
		&\geq& 2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot l(t) dt - \int_0^T \eta_t^{b_2} dt.
	\end{IEEEeqnarray*}
	where the inequalities are justified by the fact that $-A^{\eta}$, $C^{\eta}$, $D^{\eta} $, $t \mapsto \eta_t^{b_2}$ and $t \mapsto l(t)$ are all positive.	By rearranging the terms we obtain:
	\begin{equation}
		b_2 \int_0^T B^{\eta, b_2} ( \eta_t^{b_2} )^2 \cdot \left( \int_0^t e^{-2B^{\eta,b_2} \int_{s}^{t} \eta_u du} ds \right) dt  \leq  \int_0^T b_2 \eta_t^{b_2} dt
	\label{eq:l(t)_transformation_b2_infinity}
	\end{equation}

>>>>

	We assume in the following that $b_2 \geq b_2^{*,basic} := \max \{b_2^{*,u,lower}, b_2^{*,\eta,lower}, b_2^{*,upper} \}$, as defined prior to Case 1. Therefore, $s \mapsto u_s^{b_2}$, $s \mapsto w_s^{b_2}$ and $s \mapsto \eta_s^{\eta}$ are increasing functions. Moreover, from inequalities (\ref{eq:ut_uniform_lower_bound_b2_infinity})-(\ref{eq:ut_wt_upper_bound_b2_infty}), we have $b_2 u_t^{b_2} \geq m_u>0$, $b_2 \eta_t^{b_2} \geq m_\eta>0$, and $\eta_t^{b_2} \leq M<\infty$, for all $t\in[0,T]$.\\

@@

	Step 2: We derive an upper bound for $b_2 SC^{MKV,b_2}$. From equation (\ref{eq:SC_MKV_2}), we have: 
	\begin{equation}
	b_2 SC^{MKV,b_2} 	=  \underbrace{ \left[ \frac{q + \bar{q}}{2} \int_0^T b_2 v_t dt + \frac{q_T + \bar{q}_T}{2} b_2 v_T + \frac{b_2}{2} w_0^{b_2} (\mathbb{E}(\xi) )^2 \right] }_\text{\large{$=:J_1$}}  + \underbrace{ \frac{1}{2} \int_{0}^T  B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot b_2 v_t dt }_\text{\large{$=:J_2$}}
	\label{eq:J1_plus_J2_b2_infinity}
	\end{equation}	
	We also notice the following two technical results which are useful for deriving upper bounds for $J_1$ and $J_2$.	
	Let $\kappa_5 := \frac{2 m_{\eta}}{r + \bar{r}}>0$ and $\displaystyle l(b_2,t): = \int_0^t e^{- 2 B^{\eta,b_2} \int_s^t \eta^{b_2}_u du} ds$. Since $b_2 \eta_t \geq m_\eta$ for all $t \in [0,T]$, we have:
	\begin{equation}
		b_2 \cdot l(b_2,t) \leq b_2 \int_0^t \exp \left(- 2 \frac{b_2}{r + \bar{r}} m_\eta \cdot (t- s) \right) ds = \frac{1}{\kappa_5} (1 - e^{- \kappa_5 b_2 t}) \leq \frac{1}{\kappa_5}, \quad \forall \  t \in [0,T].
	\label{eq:l(t)_upper_bound_b2_infinity}
	\end{equation}
	Besides, with Riccati equation (\ref{eq:riccati_etat}) of $\eta_t^{b_2}$ and the formula of integration by parts, we deduce:
	\begin{IEEEeqnarray*}{rCL}
		 \int_0^T B^{\eta, b_2} (\eta_t^{b_2} )^2 \cdot l(t) dt 
		&= & \int_0^T  (\eta_t^{b_2})' \cdot l(t) dt + \int_0^T \left( -2A^{\eta} \eta_t^{b_2} + C^{\eta} \right) \cdot l(t) dt \nonumber \\
		&\geq & \left[ \eta_T^{b_2} l(T) - \eta_0^{b_2} l(0) - \int_0^T \eta_t^{b_2} \cdot (l(t))' dt \right]  \nonumber \\
		&= & - \int_0^T \eta_t^{b_2} \cdot \left[ l(t)\cdot( - 2 B^{\eta,b_2} \eta_t^{b_2} ) + 1 \right] dt + l(T) D^{\eta} \nonumber \\
		&\geq& 2 \int_0^T B^{\eta,b_2} (\eta_t^{b_2})^2 \cdot l(t) dt - \int_0^T \eta_t^{b_2} dt.
	\end{IEEEeqnarray*}
	where the inequalities are justified by the fact that $-A^{\eta}$, $C^{\eta}$, $D^{\eta} $, $t \mapsto \eta_t^{b_2}$ and $t \mapsto l(t)$ are all positive.	By rearranging the terms we obtain:
	\begin{equation}
		b_2 \int_0^T B^{\eta, b_2} ( \eta_t^{b_2} )^2 \cdot \left( \int_0^t e^{-2B^{\eta,b_2} \int_{s}^{t} \eta_u du} ds \right) dt  \leq  \int_0^T b_2 \eta_t^{b_2} dt
	\label{eq:l(t)_transformation_b2_infinity}
	\end{equation}
